Contracts for unions and intersections are hard for Nickel

### 2021-05-28 paper.tex
Small changes

Contracts have another perk: they correspond to the type casts of gradual
typing, a discipline for mixing static and dynamic typing in the same language.
As such, they are a precious ingredient for handling the interaction of
statically typed and dynamically typed code. While we focused on the writing of
configuration, Nickel is a proper programming language that is also designed to
write generic and reusable library code. There, the typing trade-off is
different, and static typing is more adapted. Nickel has a gradual type system,
which is yet another argument for having contracts. Let us end this section by
stressing the following points:
\begin{itemize}
    \item \textbf{Even in a purely dynamically typed language, contracts are an
        appealing feature for validation and correctness}. The gradual
        typing part deserved to be mentioned, but is is out of the scope of this
        paper.
    \item \textbf{User-defined contracts are essential for validation}. Some
        contract systems (as the one of~\cite{RootCauseOfBlame}, that will be
        extensively discussed later in the paper) do not feature user-defined
        contracts.  Rather, a fixed set of built-in contracts such as
        \nickel{Number} or \nickel{String} are provided, very much like base
        types. The absence of user-defined contracts is understandable when
        using contracts as a dynamic typing discipline for correctness. But a
        system without user-defined contracts is limited in the same way as
        static typing with respect to validation.
\end{itemize}

@@

\subsection*{Lazyness}
Evaluation strategies relates to the evaluation of the expression bound to
identifiers. Expressions are be bound by assignments (e.g. the \nickel{blah} construct in Nickel), or arguments are bound to
parameters in a function application. We will use Figure~\ref{} as a working
example.

>>>>

Contracts have another perk: they correspond to the type casts of gradual
typing, a discipline for mixing static and dynamic typing in the same language.
As such, they are a precious ingredient for handling the interaction between 
statically typed and dynamically typed code. While we focused on the writing of
configuration, Nickel is a proper programming language that is also designed to
write generic and reusable library code. There, the typing trade-off is
different, and static typing is more adapted. Nickel has a gradual type system,
which is yet another argument for having contracts. Let us end this section by
stressing the following points:
\begin{itemize}
    \item \textbf{Even in a purely dynamically typed language, contracts are an
        appealing feature for validation and correctness}. The gradual typing
        part enters the general picture but is out of the scope of this paper.
    \item \textbf{User-defined contracts are essential for validation}. Some
        contract systems (as the one of~\cite{RootCauseOfBlame}, that will be
        extensively discussed later in the paper) do not feature user-defined
        contracts.  Rather, a fixed set of built-in contracts such as
        \nickel{Number} or \nickel{String} are provided, very much like base
        types. The absence of user-defined contracts is understandable when
        using contracts as a dynamic typing discipline for correctness. But a
        system without user-defined contracts is limited in the same way as
        static typing with respect to validation.
\end{itemize}

@@

\subsection*{Lazyness}
Evaluation strategies relates to the evaluation of the expression bound to
identifiers. Expressions are be bound by assignments (e.g. let bindings in
Nickel), or by function applications (arguments are bound to parameters). We
will use Figure~\ref{} as a working example.
